### 2014-12-02 reports/report.Rmd
Simplify country plotting code. #191

```{r world_map, echo=FALSE, fig.width=12, fig.height=10}
map_info <- prep_map_info(data_study$data, study_name)
drawWorldPlot(map_info)
```

@@

```{r country_map, echo=FALSE, fig.width=12, fig.height=10}
report_missing_info(map_info)
drawCountryPlot(map_info)
```

>>>>

```{r world_map, echo=FALSE, fig.width=12, fig.height=10}
drawWorldPlot(data_study$data)
```

@@

```{r country_map, echo=FALSE, fig.width=12, fig.height=10}
map_sites_all_countries(data_study$data)
```
